D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-01-23 ootavacuous.tex
Add links to C and C++ proposals for side-effect definition
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Many projects' coding guidelines prohibit side effects in expressions,
their goal being to obtain portable code whose behavior does not depend
on arbitrary choices on the part of the implementation.
However, the above code nevertheless conforms to the standard.

>>>>

Many projects' coding guidelines prohibit side effects in expressions,
their goal being to obtain portable code whose behavior does not depend
on arbitrary choices on the part of the implementation.
However, the above code nevertheless conforms to the standard.
Note that side effects in expressions lacking sequence points is
undefined behavior, however, there are proposals to define it in
the C++ and C languages, allowing implementations to nevertheless reorder
evaluation when permitted by the as-if rule.\footnote{
	\url{https://www.open-std.org/jtc1/sc22/wg21/docs/papers/2016/p0145r3.pdf}
	\url{https://www.open-std.org/jtc1/sc22/wg14/www/docs/n3203.htm}}
